### 2021-04-22 paper/ase21/report/abstract.tex
[ASE21] Draft of report

\begin{abstract}
  In this report, we formally define a modified $\ires$ with its syntax and
  semantics.  Moreover, we define type analysis for the modified $\ires$.
\end{abstract}

>>>>

\begin{abstract}
  This technical report is a companion report of the research paper for $\tool$,
  a JavaScript Specification Type Analyzer using Refinement.  In this report, we
  formally define the syntax and semantics of a modified $\ires$, an untyped
  intermediate representation for ECMAScript.  Moreover, we formally define type
  analysis for the modified $\ires$ based on the abstract interpretation
  framework with flow- and type-sensitivity for arguments.  To increase the
  precision of the type analysis, we also present \textit{condition-based
  refinement} for type analysis, which prunes out infeasible abstract states
  using conditions of assertions and branches.
\end{abstract}
